Inferring the distribution and rate of Earth-like exoplanets \\ from noisy individual-planet inferences

### 2014-05-14 document/ms.tex
chain stats
some words about transit probability

@@

\dfmtodo{Talk about how we apply the geometric transit probability.}

>>>>

For all the results below, we run a Markov chain with $10^6$ steps for the bin
heights and update the hyperparameters every 10 steps.
We discard the first \dfmtodo{XXXX} samples as burn-in and then use the
remaining samples as an approximation to the marginalized probability
distribution for \ratepars.
We tune the Metropolis--Hastings proposal used to update the hyperparameters
by hand to get an acceptance fraction of $\sim0.2-0.4$ for those parameters.

@@

The detection efficiency also depends on the geometric transit probability
$R_\star/a$.
Since we're modeling the distribution in the period--radius plane, we need to
compute the transit probability marginalized over stellar radius and mass.
This marginalized distribution scales only with the period of the orbit as
\dfmtodo{$\propto \period^{3/2}$}.
In theory, this marginalization should be over the true distribution of these
parameters in the selected stellar catalog but we'll approximate it by
the empirical distribution.
